Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-29 Article/main.tex
Finished Findings + Limitations

While this case study made use of instructional theory targeted towards preschool children\cite{allers2021children, callaghan2018}

\begin{table}[htbp]
\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.0cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

@@

\section{Limitations and Future Research}

>>>>

While this case study\cite{allers2021children} made use of instructional theory targeted towards preschool children\cite{matthews2007,callaghan2018} some the frameworks and learning theory used can also be applied to all serious games. The first design principle followed was \textit{simplicity} as it allows a user to follow the content adequately and as such learn effectively\cite{allers2021children}. This principle is specified to the success of a awareness campaign however can also be applied to a serious game as, depending on the specific level of education, simplicity is vitally important. 
The study goes on to cite Matthews \textit{et al.}\cite{matthews2007} on the ways children tend to learn. This includes:
\begin{itemize}
\item Observation
\item Listening
\item Exploring
\item Experimentation
\item Asking questions
\end{itemize}
\vspace*{\baselineskip}

Learning through play, such as a serious game, is an effective way to implement all of these methods\cite{allers2021children} and as such provides an additional framework targeted specifically at younger children as opposed to the previous studies\cite{Dincelli2020,Sheng2007} which were focused on adults. While this list does not provide direct principles to follow during the design process, including ways for these methods of learning to be present in a serious game should also be taken into consideration.
\\\\
In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based off how young children, namely preschoolers, learn. The first of these is \textit{clear and simple goals} which is concerned with presenting a user with concise outcomes to work towards\cite{callaghan2018}. Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example preschoolers may not yet be able to read and as such the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}. The next element is \textit{Structure of the challenge} consists of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}. This element can also be described using some of the corollaries from Merril's First Principles\cite{Merrill2002} - which will be discussed in the following section. The last element Callaghan \textit{et al.}\cite{callaghan2018} is that of \textit{Motion based learning} which describes the physical interaction a user will have with applications which in this case would be designing larger touch controls to account for a preschool child's current level of motor functions. This particular aspect is almost certainly vital when dealing with any knowledge from the psycho motor domain.
\\\\
As previously mentioned, this case study has not yet developed the serious game and as such cannot be tested by users. However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.
\\\\

\begin{table}[htbp]
\caption{Design Principles Defined by Case Study (Summarised) \cite{Dincelli2020,Sheng2007,allers2021children}}
\begin{adjustwidth}{-0.0cm}{}
\begin{tabular}{|c|c|c|c|}
\hline

@@

\section{Limitations and Future Research}
This study made use of various fields of study as well as case studies of serious games and their design in order to answer the question posed. The current limitations of answering the question largely center around the amount of literature sourced. In terms of the fields looked at (pedagogy, ludology and gamification) these seem to be sufficient in terms of what literature can be used and as such it is the specific literature used that imposes limitations. There are many more instructional theories that could be considered and as such future research could delve into more theories and expand the knowledge base used to answer the question. Another limitation comes from the case studies used. All of the main case studies discussed in this article had a focus on computer security to varying degrees. Due to this, future research could include case studies on the design, implementation or development of serious games in other fields.
\\\\
Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned. This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based of the synthesis provided or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.

\section{Conclusion}
